---
title: "Assets_Performance Various Sectors"
author: "Mandar"
date: "2022-08-02"
output:
  html_document:
    code_folding: show
    df_print: paged
    highlight: tango
    number_sections: yes
    theme: flatly
    toc: yes
    toc_depth: 2
    
---

```{r}
knitr::opts_chunk$set(
    echo = FALSE,
    message = FALSE,
    warning = FALSE,
    out.width = "200%",
    out.height = "500px",
    fig.pos = "center",
    dpi = 300)
```


```{r}
# Loading the libraries

library(tidyverse)
library(lubridate)
library(tidyquant)
library(plotly)
library(broom)
library(skimr)
library(DataExplorer)

```
# Getting the data for IT/TECH sector
## We need those companies , which have been listed before 1990.

```{r}
symbols_tech <- c("AAPL","IBM","MSFT","ORCL","ADBE")

Tech_Prices <- symbols_tech %>%
    tq_get(get = "stock.prices", from = "1990-01-01") 

returns_tech <- Tech_Prices %>%
    group_by(symbol) %>%
    select(symbol, date, adjusted) %>%
    tq_transmute(select     = adjusted,
                 mutate_fun = periodReturn,
                 period     = "monthly",
                 col_rename = "Tech") %>%
    ungroup() %>%
    mutate(date = rollback(date, roll_to_first = TRUE))

end_date <-  last(returns_tech)


```
# Visualization

```{r}
returns_tech %>%
    ggplot(aes(x= Tech)) +
    geom_density(aes(colour = symbol), alpha = 1) +
    geom_histogram(aes(fill = symbol), alpha = 0.45, binwidth = .005) +
    guides(colour = FALSE) +
    theme_tq() + labs(
        title = "Spread of  Returns for selected Tech Stocks",
        subtitle = "Top Tech Stocks Monthly Returns from 1990:2022"
        
    ) + ylab("Count") +xlab("Monthly_Returns") + theme(legend.position = "none") +
    facet_wrap(~ symbol) +
    scale_y_continuous() + scale_x_continuous(labels = scales::percent)
```
```{r}
g <- returns_tech %>%
    ggplot(aes(date, Tech, color = symbol)) +
    geom_line() + facet_wrap(~symbol) +
    theme_tq() + scale_color_tq(theme = "light") +
    scale_y_continuous(labels = scales::percent) +
    labs(
        title = "Monthly Returns of Selected Tech Stocks ",
        subtitle = " Volatility observed in 2000,and  in 2008/2009",
        y = "Monthly Returns",
        x = ""
    ) + theme(legend.position = "none")

ggplotly(g)
```
# We visualize the stock prices to see the trend
```{r}
K <- Tech_Prices %>%
    ggplot(aes(date, adjusted, color = symbol)) +
    geom_line() + facet_wrap(~symbol, scales = "free_y") +
    scale_y_continuous(labels = scales::dollar) +
     theme_tq() + scale_color_tq(theme = "dark") +
    labs(
        title = "Stock Prices of selected Tech Stocks",
        subtitle = " We observe a rising trend ",
        y = "Adjusted Stock Price",
        x = ""
    ) +
    theme(legend.position = "none")
    
    
ggplotly(K)
    
```
# We use the returns to measure the individual sharpe ratio
```{r}
returns_tech %>%
    group_by(symbol) %>%
    tq_performance(Ra = Tech,
                   performance_fun = SharpeRatio.annualized,
                   scale = 12,
                   Rf = 0.03/12)  %>%
    ungroup() %>%
    mutate(symbol = as.factor(symbol)) %>%
    mutate(`AnnualizedSharpeRatio(Rf=3%)` = round(`AnnualizedSharpeRatio(Rf=3%)`, 2)) %>%
    ggplot(aes(symbol, `AnnualizedSharpeRatio(Rf=3%)`, label = `AnnualizedSharpeRatio(Rf=3%)`)) +
    geom_col(fill = "#2c3e50") +
    theme_tq() +
    scale_color_tq(theme = "light") +
    geom_label(nudge_y = -0.01) +
    labs(title = "Annualized Sharpe Ratio (RFR = 3%)",
         subtitle = "IBM has the lowestsharpe ratio while Microsoft has the highest",
         caption = "Selected Tech Stocks ",
         y = "Sharpe Ratio",
         x = "")

```
# We now create a portfolio for Tech Stocks with equal weighted scheme

# Step 1 using equal weights 
```{r}
n <- length(symbols_tech)
w <- rep(1/n,n)
wts_tbl <- tibble(symbols_tech,w)
wts_tbl
```
```{r}
wts_tbl %>% 
    ggplot(aes(x = "", y = w, fill = symbols_tech)) + 
    geom_bar(width = 1, stat = "identity") + 
    coord_polar("y", start = 0) + 
    theme(axis.text.x = element_blank()) +
    geom_text(label = scales::percent(w), position = position_stack(vjust = 0.5)) +
    scale_fill_tq(theme = "light") + 
    labs(
         title = "Tech Portfolio",
         caption = " Equal Weighted"
         )
```
# step 2 now creating portfolio
```{r}
port_returns_tbl <- returns_tech %>%
    group_by(symbol) %>%
    tq_portfolio(assets_col   = symbol,
                 returns_col  = Tech,
                 weights      = wts_tbl,
                 rebalance_on = "years") %>%
    add_column(symbol ="Portfolio",.before = 1) %>%
    rename(Tech = portfolio.returns)

```
```{r}
port_returns_tbl 
```
```{r}
combined_tbl <- port_returns_tbl %>%
    rbind(returns_tech %>% group_by(symbol))


    
```
```{r}
end_port_date = last(port_returns_tbl$date)
combined_tbl %>%
    ggplot(aes(date, Tech)) +
    geom_smooth(data = port_returns_tbl,
                aes(color = symbol),
                se = FALSE,
                linetype= "dashed",
                colour = "blue") +
    geom_smooth(data = returns_tech,
                aes(colour = symbol),
                se = FALSE,
                linetype= "solid"
                ) +
    scale_y_continuous() + theme_tq() + scale_color_tq(theme = "light") +
    scale_y_continuous(labels = scales::percent) +
    labs(title = "Monthly Returns of Portfolio vs Individual Stocks",
         subtitle = "Portfolio is the dashed blue line",
         y = "Monthly Returns") +
    annotate(geom = "text",
             x = end_port_date,
             y = 0.02,
             label = "Portfolio",
             fontface = "plain")
```
```{r}
combined_tbl %>%
    group_by(symbol) %>%
    tq_performance(Ra = Tech,
                   performance_fun = SharpeRatio.annualized,
                   scale = 12,
                   Rf = 0.03 / 12) %>% 
    ungroup() %>%
    mutate(symbol = as.factor(symbol)) %>%
    mutate(`AnnualizedSharpeRatio(Rf=3%)` = round(`AnnualizedSharpeRatio(Rf=3%)`, 2)) %>%
    ggplot(aes(symbol, `AnnualizedSharpeRatio(Rf=3%)`, label = `AnnualizedSharpeRatio(Rf=3%)`)) +
    geom_col(fill = "#2c3e50") +
    theme_tq() + scale_color_tq(theme = "light") +
    geom_label(nudge_y = -0.01) +
    labs(
        title = "Annualized Sharpe Ratio",
        subtitle = "Portfolio has the highest Sharpe Raito ",
        caption = "Selected Tech Stocks",
        x ="", y = "Sharpe Ratio"
    )
```

# lets see the investment over the period of time, for that we have to add wealth index in the portfolio 
```{r}

investment_tbl <- returns_tech %>%
    group_by(symbol) %>%
    tq_portfolio(
        assets_col  = symbol,
        returns_col = Tech,
        weights     = wts_tbl,
        wealth.index = TRUE ) %>%
    mutate(investment_growth = portfolio.wealthindex  * 1000)

    
```
#Visualization of Investment growth for our portfolio
```{r}
  investment_tbl %>%
    ggplot(aes(date, investment_growth)) +
    geom_line(stat = "identity") +
    theme_tq() + scale_color_tq(theme = "light") +
    scale_color_tq() +
    scale_y_continuous(labels = scales::dollar) +
    labs(
        title = "Investment Growth of Portfolio for an Investment of $1000",
        subtitle = "Equal Weight Allocation",
        caption = "Selected Tech Stocks",
        x ="",
        y = "Investment Growth"
    )
    
```
```{r}
I <- investment_tbl %>%
    ggplot(aes(date, investment_growth)) +
    geom_line(stat = "identity") +
    theme_tq() + scale_color_tq(theme = "light") +
    scale_color_tq() +
    scale_y_continuous(labels = scales::dollar) +
    labs(
        title = "Investment Growth of Portfolio for an Investment of $1000",
        subtitle = "Equal Weighted Portfolio ",
        caption = "Selected Tech Stocks",
        x ="",
        y = "Investment Growth"
    )
ggplotly(I)
```
```{r}
w_2 <- c(0.2, 0.2, 0.2, 0.2, 0.2,
         1, 0, 0, 0, 0,
         0, 1, 0, 0, 0,
         0, 0, 1, 0, 0,
         0, 0, 0, 1, 0,
         0, 0, 0, 0, 1)
weights_tbl <- tibble(symbols_tech) %>% 
    tq_repeat_df(n = 6) %>% 
    bind_cols(tibble(w_2)) %>%
    group_by(portfolio)
```
```{r}
weights_tbl %>% 
    ungroup() %>% 
    mutate(w_2 = paste0(w_2*100, "%")) %>% 
    pivot_wider(names_from = symbols_tech, values_from = w_2) %>% 
    mutate(portfolio = case_when(portfolio == 1 ~ "Tech Portfolio",
                                 portfolio == 2 ~ "AAPL",
                                 portfolio == 3 ~ "IBM",
                                 portfolio == 4 ~ "MSFT",
                                 portfolio == 5 ~ "ORCL",
                                 portfolio == 6 ~ "ADBE")) 
```
```{r}
returns_multi_tbl <- returns_tech %>%
    tq_repeat_df(n = 6)


port_investment_tbl <- returns_multi_tbl %>% 
    tq_portfolio(assets_col = symbol,
                 returns_col = Tech,
                 weights = weights_tbl,
                 wealth.index = TRUE) %>% 
    mutate(investment.growth = portfolio.wealthindex * 1000)
```
```{r}
port_investment_tbl %>%
    ungroup() %>% 
    mutate(portfolio = case_when(portfolio == 1 ~ "Tech Portfolio",
                                 portfolio == 2 ~ "AAPL",
                                 portfolio == 3 ~ "IBM",
                                 portfolio == 4 ~ "MSFT",
                                 portfolio == 5 ~ "ORCL",
                                 portfolio == 6 ~ "ADBE")) %>% 
    mutate(portfolio = as.factor(portfolio)) %>% 
    ggplot(aes(x = date, y = investment.growth, colour = portfolio)) + 
    geom_line(stat = "identity") + 
    theme_tq() + 
    scale_color_tq() + 
    scale_y_continuous(labels = scales::dollar) + 
    labs(title = "Tech Portfolio Growth vs Standalone Security Growth",
         subtitle = "Equal Weight Allocation",
         caption = "Selected Stocks",
         x = "",
         y = "Investment Growth") +
    annotate(geom = "text",
             x = last(port_investment_tbl$date),
             y = 344000,
             label = "Portfolio",
             fontface = "plain")
```
# Using high charter
```{r}
library(timetk)
high_chart_xts <- port_investment_tbl %>%
    ungroup() %>% 
    mutate(portfolio = case_when(portfolio == 1 ~ "Tech Portfolio",
                                 portfolio == 2 ~ "AAPL",
                                 portfolio == 3 ~ "IBM",
                                 portfolio == 4 ~ "MSFT",
                                 portfolio == 5 ~ "ORCL",
                                 portfolio == 6 ~ "ADBE"))%>% 
    select(-portfolio.wealthindex) %>% 
    pivot_wider(names_from = portfolio, values_from = investment.growth) %>% 
    tk_xts(date_var = date,
           silent = TRUE)
```
```{r}
library(highcharter)
highchart(type = "stock") %>% 
    hc_title(text = "Tech Portfolio Growth vs Standalone Security Growth") %>% 
    hc_add_series(high_chart_xts[, 1], 
                  name = "Portfolio") %>% 
    hc_add_series(high_chart_xts[, 2],
                  name = symbols_tech[1]) %>% 
    hc_add_series(high_chart_xts[,3],
                  name = symbols_tech[2]) %>% 
    hc_add_series(high_chart_xts[,4],
                  name = symbols_tech[3]) %>% 
    hc_add_series(high_chart_xts[,5],
                  name = symbols_tech[4]) %>% 
    hc_add_series(high_chart_xts[,6],
                  name = symbols_tech[5]) %>%
    # hc_tooltip(pointFormat = '{series.name}
    #            ${point.y:,.0f}')
    hc_tooltip(pointFormat =
    "<span style=\"color:{series.color}\">{series.name}</span>:<b>${point.y:,.0f}</b><br/>",
        shared=TRUE)
```
```{r}
sessionInfo()
```







